Arrows for Parallel Computation

### 2018-01-07 paper/content/arxiv/ms.tex
minor edits in biblio

\bibitem[\protect\citename{Aljabri {\em et~al.}\relax,
  }2014]{Aljabri:2013:DIG:2620678.2620682}
Aljabri, Malak, Loidl, Hans-Wolfgang, \& Trinder, Phil~W. (2014).
\newblock The design and implementation of {GUMSMP}: A multilevel parallel
  haskell implementation.
\newblock {\em Pages  37:37--37:48 of:} {\em Proceedings of the 25\xth
  Symposium on Implementation and Application of Functional Languages}.
\newblock IFL '13.
\newblock ACM.

@@

\bibitem[\protect\citename{Keller {\em et~al.}\relax,
  }2010]{Keller:2010:RSP:1932681.1863582}
Keller, Gabriele, Chakravarty, Manuel~M.T., Leshchinskiy, Roman, {Peyton
  Jones}, Simon, \& Lippmeier, Ben. (2010).
\newblock Regular, shape-polymorphic, parallel arrays in haskell.
\newblock {\em Sigplan not.}, {\bf 45}(9), 261--272.

@@

\bibitem[\protect\citename{Svensson, }2011]{obsidian-phd}
Svensson, Joel. (2011).
\newblock {\em Obsidian: Gpu kernel programming in haskell}.
\newblock Ph.D. thesis, Chalmers University of Technology.

>>>>

\bibitem[\protect\citename{Aljabri {\em et~al.}\relax,
  }2014]{Aljabri:2013:DIG:2620678.2620682}
Aljabri, Malak, Loidl, Hans-Wolfgang, \& Trinder, Phil~W. (2014).
\newblock The design and implementation of {GUMSMP}: A multilevel parallel
  Haskell implementation.
\newblock {\em Pages  37:37--37:48 of:} {\em Proceedings of the 25\xth
  Symposium on Implementation and Application of Functional Languages}.
\newblock IFL '13.
\newblock ACM.

@@

\bibitem[\protect\citename{Keller {\em et~al.}\relax,
  }2010]{Keller:2010:RSP:1932681.1863582}
Keller, Gabriele, Chakravarty, Manuel~M.T., Leshchinskiy, Roman, {Peyton
  Jones}, Simon, \& Lippmeier, Ben. (2010).
\newblock Regular, shape-polymorphic, parallel arrays in Haskell.
\newblock {\em Sigplan not.}, {\bf 45}(9), 261--272.

@@

\bibitem[\protect\citename{Svensson, }2011]{obsidian-phd}
Svensson, Joel. (2011).
\newblock {\em Obsidian: GPU kernel programming in Haskell}.
\newblock Ph.D. thesis, Chalmers University of Technology.
